Capstone Movielens Report

### 2025-11-06 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Capstone Report: `Overall Mean Rating (OMR) Model` section completed..

Let's begin our analysis by evaluating the simplest model described in [Section 25.1 *Case study: recommendation systems / A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook*[@IDS2_25-1], and then gradually refine it through further research.

>>>>

Let's begin our analysis by evaluating the simplest model described in [Section 25.1 *Case study: recommendation systems / A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook (New Edition)*[@IDS2_25-1], and then gradually refine it through further research.
